---
title: "Optional Project"
author: "J.E. Panzik"
date: "6/2/2020"
output: html_document
---

```{r loaddata}
#install.packages("devtools")
devtools::install_github("jhudsl/collegeIncome")
library(collegeIncome)
data(college)
data <- college
```

```{r matahari}
devtools::install_github("jhudsl/matahari")
library(matahari)
```

```{r dancestart}
dance_start(value = FALSE, contents = FALSE)
```

```{r data view}
head(data,3)
```

Subset the data to look at the impacts of variables on the median, p25th, and p75th salaries.

```{r subsets}
data$major_category <- as.factor(data$major_category)
dataMedian <- data[,c("major_category", "perc_women", "median", "perc_men", "perc_employed_fulltime_yearround")]
data25 <- data[,c("major_category", "perc_women", "p25th", "perc_men", "perc_employed_fulltime_yearround")]
data75 <- data[,c("major_category", "perc_women", "p75th", "perc_men", "perc_employed_fulltime_yearround")]
```


Fit median, p25th, and p75th salaries to all variables first, then use step to determine which variable(s) is/are the most significant.
```{r fits}
fitMedAll <- lm(median~., data=dataMedian)
summary(fitMedAll)
fitMedOpt <- step(fitMedAll, direction="both", trace=FALSE)
summary(fitMedOpt)

fit25All <- lm(p25th~., data=data25)
summary(fit25All)
fit25Opt <- step(fit25All, direction="both", trace=FALSE)
summary(fit25Opt)

fit75All <- lm(p75th~., data=data75)
summary(fit75All)
fit75Opt <- step(fit75All, direction="both", trace=FALSE)
summary(fit75Opt)

fitAllYear <- lm(perc_employed_fulltime_yearround~major_category, data=data25)
summary(fitAllYear)
```

Analysis shows that major category holds litle influence on the median, p25th, and p75th salaries. Majors that are able to put more of their students in full-time, year-round employment have greater median, p25th, and p75th salaries.
```{r dancesave}
dance_save("college_major_analysis.rds")
```